\section{Methods} \label{sec:methods}
To address this text classification task we first tried the most widely used text representations and classifiers.
We tried representations based on lexical features as Bag Of Words \cite{harris1954distributional},Bag Of N-Grams (bigrams and trigrams), both with and without with TF-IDF normalization.
As classifiers we tried Random Forest, Decision Trees, Support Vector Machines and MultiLayer Perceptron, but since that results obtaines with the combination of those tecniques were outperformed by neural models, we decided not to report those in the paper.
Bag of words

\section{Representation}
To represent to tweet fed into the classifier we decided to used word embeddings,which is a tecnique where elements (in out case words and n-grams) are mapped into a vector of real numbers.
The whole sentence is mapped into a matrix with dimension sentence lenght x embedding dimension.
We left the sentence length as a parameter and the best results were obtained with length=30, that's reasonable since the average tweet length in words in 24.

\subsection{Words vectors}
Since the number of tweets is considered small to learn vector representation of words, we tried to initialize the embedding matrix with pretrained word vectors.
In particular we used vectors trained on wikipedia using fastText \cite{bojanowski2016enriching}.
We tried static pretrained vectors ,learning them during training starting from a random matrix or from the pretrained embeddings.

\subsection{N-gram embedding}
We also tried to learn an embedding for n-grams (bigrams and trigrams), but since the corpus is small n-grams frequencies are very low and the algorithm is not able to learn a valid embedding.
Also there are no pre-trained n-grams available.
Bigrams brought a small improvement, bigger n-grams result in performance decrease.



\section{Preprocessing}
We explored different combinations of twitter pre-processing, as converting some elements such mentions, emoji, smiley, hashtags into constant string (i.e. Tokenize @Ambros and \#atoppe :) $\rightarrow $ Tokenize \$MENTION and \$HASHTAG \$SMILEY ); removeing elements as URLs, reserved words and numbers.
We also measured the contribution of stemming, stopwords and punctuation removal.
To address those pre-processing we used the following \cite{nltk} \cite{tweets-preprocessor}.


\section{Models}

In the following section we present different neural network models, each model has as first layer an embedding layer that maps words to the corresponding word vectors.


\subsection{Convolutional Neural Network}
Convolutional Neural Networks are considered state of the art in many text classification problem, this model is a

Start whith the meaning reason behind this model (e.g. LSTM because in translation is a state of the art).

Long short term memory.
Bidirectional long short term memory.

Convolutional neural network.
Hybrid convolutional neural network.

\subsubsection{Fast text.}

same and equal of original but changing the number of layer  (worstening in increasing the number of layer) + adding of the gaussian noise and batch normalization

\subsubsection{KIM.}

Pippo \cite{kim2014convolutional}



from kim model we optimize ttill the following net configuration/topology: description of the net