\begin{thebibliography}{1}

\bibitem{kim2014convolutional}
Kim, Yoon. "Convolutional neural networks for sentence classification." arXiv preprint arXiv:1408.5882 (2014).

\bibitem{joulin2016bag}
Joulin, Armand, et al. "Bag of tricks for efficient text classification." arXiv preprint arXiv:1607.01759 (2016).

\bibitem{nltk}
Edward Loper and Steven Bird. 2002. NLTK: the Natural Language Toolkit. In Proceedings of the ACL-02 Workshop on Effective tools and methodologies for teaching natural language processing and computational linguistics - Volume 1 (ETMTNLP '02), Vol. 1. Association for Computational Linguistics, Stroudsburg, PA, USA, 63-70. DOI=http://dx.doi.org/10.3115/1118108.1118117

\bibitem{tweets-preprocessor}
Preprocessor is a preprocessing library for tweet data written in Python, https://github.com/s/preprocessor

\bibitem{bojanowski2016enriching}
Bojanowski, Piotr and Grave, Edouard and Joulin, Armand and Mikolov, Tomas. "Enriching Word Vectors with Subword Information" arXiv preprint arXiv:1607.04606 (2016).

\bibitem{harris1954distributional}
Harris, Zellig S. "Distributional structure." Word 10.2-3 (1954): 146-162.

\bibitem{bazzanella2011oscillazioni}
Bazzanella, Carla. "Oscillazioni di informalità e formalità: scritto, parlato e rete." Formale e informale. La variazione di registro nella comunicazione elettronica. Roma: Carocci (2011): 68-83.

\bibitem{cerruti2013netspeak}
Cerruti, Massimo, and Cristina Onesti. "Netspeak: a language variety? Some remarks from an Italian sociolinguistic perspective." Languages go web: Standard and non-standard languages on the Internet (2013): 23-39.

% To better understand how it works go to 
% http://www.wildml.com/2015/11/understanding-convolutional-neural-networks-for-nlp/
\bibitem{zhang2015sensitivity}
Zhang, Ye, and Byron Wallace. "A sensitivity analysis of (and practitioners' guide to) convolutional neural networks for sentence classification." arXiv preprint arXiv:1510.03820 (2015).

\end{thebibliography}