\begin{thebibliography}{1}

\bibitem{kim2014convolutional}
Kim, Yoon. "Convolutional neural networks for sentence classification." arXiv preprint arXiv:1408.5882 (2014).

\bibitem{joulin2016bag}
Joulin, Armand, et al. "Bag of tricks for efficient text classification." arXiv preprint arXiv:1607.01759 (2016).

\bibitem{nltk}
Edward Loper and Steven Bird. 2002. NLTK: the Natural Language Toolkit. In Proceedings of the ACL-02 Workshop on Effective tools and methodologies for teaching natural language processing and computational linguistics - Volume 1 (ETMTNLP '02), Vol. 1. Association for Computational Linguistics, Stroudsburg, PA, USA, 63-70. DOI=http://dx.doi.org/10.3115/1118108.1118117

%\bibitem{tweets-preprocessor}
%Preprocessor is a preprocessing library for tweet data written in Python, https://github.com/s/preprocessor

\bibitem{bojanowski2016enriching}
Bojanowski, Piotr and Grave, Edouard and Joulin, Armand and Mikolov, Tomas. "Enriching Word Vectors with Subword Information" arXiv preprint arXiv:1607.04606 (2016).

\bibitem{harris1954distributional}
Harris, Zellig S. "Distributional structure." Word 10.2-3 (1954): 146-162.

\bibitem{bazzanella2011oscillazioni}
Bazzanella, Carla. "Oscillazioni di informalità e formalità: scritto, parlato e rete." Formale e informale. La variazione di registro nella comunicazione elettronica. Roma: Carocci (2011): 68-83.

\bibitem{cerruti2013netspeak}
Cerruti, Massimo, and Cristina Onesti. "Netspeak: a language variety? Some remarks from an Italian sociolinguistic perspective." Languages go web: Standard and non-standard languages on the Internet (2013): 23-39.

% To better understand how it works go to 
% http://www.wildml.com/2015/11/understanding-convolutional-neural-networks-for-nlp/
\bibitem{zhang2015sensitivity}
Zhang, Ye, and Byron Wallace. "A sensitivity analysis of (and practitioners' guide to) convolutional neural networks for sentence classification." arXiv preprint arXiv:1510.03820 (2015).

\bibitem{bosco2016}
C. Bosco, M. Lai, V. Patti, F. Rangel, P. Rosso (2016) Tweeting in the Debate about Catalan Elections. In: Proc. LREC workshop on Emotion and Sentiment Analysis Workshop (ESA), LREC-2016, Portorož, Slovenia, May 23-28, pp. 67-70.

\bibitem{rangel2016overview}
F. Rangel, P. Rosso, B. Verhoeven, W. Daelemans, M. Potthast, B. Stein (2016) Overview of the 4th Author Profiling Task at PAN 2016: Cross-Genre Evaluations. In: Balog K., Cappellato L., Ferro N., Macdonald C. (Eds.) CLEF 2016 Labs and Workshops, Notebook Papers. CEUR Workshop Proceedings. CEUR-WS.org, vol. 1609, pp. 750-784.

\bibitem{mohammad2016stance}
Mohammad, Saif M., Parinaz Sobhani, and Svetlana Kiritchenko. "Stance and sentiment in tweets." arXiv preprint arXiv:1605.01655 (2016).

\bibitem{mohammad2016semeval}
Mohammad, Saif M., et al. "Semeval-2016 task 6: Detecting stance in tweets." Proceedings of SemEval 16 (2016).

\bibitem{yu2015multi}
Fisher Yu, Vladlen Koltun , “Multi-Scale Context Aggregation by Dilated Convolutions”

%Taulé M., Martí M.A., Rangel F., Rosso P., Bosco C., Patti V. 
%Overview of the task of Stance and Gender Detection in Tweets on Catalan Independence at IBEREVAL 2017. 
%In: Notebook Papers of 2nd SEPLN Workshop on Evaluation of Human Language Technologies for Iberian Languages (IBEREVAL), Murcia, Spain, September 19, CEUR Workshop Proceedings. CEUR-WS.org, 2017

\end{thebibliography}